---
title: "p8105_hw1_rx2236"
author: "Ruiqi Xue"
date: "2023-09-19"
output: github_document
---
```{r}
library(tidyverse)
```



```{r}
library(moderndive)

data("early_january_weather")

  
```


## Problem 1
### Data description
This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` variables/columns.
The variables are `r names(early_january_weather)`.

The `origin` variable is where the weather station locates. In this dataset, the only value for this variable is `r unique(early_january_weather["origin"])`.

The `year`, `month`, `day` and `hour` variables are time of recording. 
In this dataset, the only value of `year` is `r unique(early_january_weather["year"])` and the only value of `month` is `r unique(early_january_weather["month"])`. 
Value of `day` ranges from `r range(early_january_weather["day"])` and value of `hour` ranges from `r range(early_january_weather["hour"])`. 

So this dataset shows weather information of EWR airport in the first 15 days of January in 2013.

The `temp` and `dewp` represent temperature and dewpoint in F. The average temperature is `r mean(early_january_weather$"temp")` F and temperature ranges from `r range(early_january_weather$temp)` F. 

The `humid` variable represents the relative humidity which has an average value `r mean(early_january_weather$"humid")`.
The `wind_dir`, `wind_speed` and `wind_gust` represent wind direction (in degrees), speed and gust speed (in mph).

The `precip` represents the precipitation (in inches), `pressure` represents sea level pressure in millibars, and `visib` represents visibility (in miles).

Finally, the `time_hour` is the date and hour of the recording as a POSIXct date.

### Making plot
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
```

Apparent patterns in this plot include temperature fluctuates periodically, with a increasing tendency. When temperature rises, the humidity usually rises, and when temperature drops, the humidity drops as well in the overall picture. Generally the humidity is higher in the second half of the recorded time period.

```{r}
ggsave("scatterplot.pdf")
```

## Problem 2
### Create dataframe
```{r}
p2_df = 
  tibble(
    num_samp = rnorm(10),
    log_vec = num_samp > 0,
    cha_vec = c('a', 'b', 'c', 'd', 'e', 'f', 'g', 'h', 'i', 'j'),
    factor_vec = factor(rep_len(c(1, 2, 3), 10))
  )
```

### Take means
```{r}
mean(pull(p2_df, num_samp))
mean(pull(p2_df, log_vec))
mean(pull(p2_df, cha_vec))
mean(pull(p2_df, factor_vec))
```










